---
title: "data exploration"
author: "Caitlyn Clendenin"
date: "11/29/2020"
output: html_document
---

## Initial Police Data Exploration

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
policedata <- read.csv("~/Downloads/policearrest.csv")
```

For my own purposes, the list of variable names and their meaning are below:
- CCR : incident number
- AGE : age of suspect
- GENDER : gender of suspect
- RACE : race of suspect
- ARREST_DATE : date of arrest
- ARREST_TIME : time of arrest
- ARRESTLOCATION : location of arrest 
- OFFENSES : all offenses listed for the incident 
- INCIDENTLOCATION : incident location
- NEIGHBORHOOD : neighborhood 
- ZONE : police zone where incident occurred
- X : The geocoded X coordinate of the incident location
- Y : The geocoded Y coordinate of the incident location

```{r}
head(policedata)
summary(policedata)
```

## Histogram of Age Groups 
```{r}
hist(policedata$AGE, xlim = c(0,90), breaks = 150, col = "slategrey", 
     xlab = "Age", main = "Histogram of Arrests")
```






