---
title: "data exploration"
author: "Caitlyn Clendenin"
date: "11/29/2020"
output:
  pdf_document: default
  html_document: default
---

## Initial Police Data Exploration

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
policedata <- data.frame(read.csv("~/Downloads/policearrest.csv"))
trafficsigns <- data.frame(read.csv("~/Downloads/pgh traffic signs.csv"))
```

For my own purposes, the list of variable names and their meaning are below:
- `CCR` : incident number
- `AGE` : age of suspect
- `GENDER` : gender of suspect
- `RACE` : race of suspect
- `ARREST_DATE` : date of arrest
- `ARREST_TIME` : time of arrest
- `ARRESTLOCATION` : location of arrest 
- `OFFENSES` : all offenses listed for the incident 
- `INCIDENTLOCATION` : incident location
- `NEIGHBORHOOD` : neighborhood 
- `ZONE` : police zone where incident occurred
- `X` : The geocoded X coordinate of the incident location
- `Y` : The geocoded Y coordinate of the incident location

### Summary Statistics 
```{r}
head(policedata)
summary(policedata)
```
One interesting takeaway is that the neighborhood with the
highest number of incidents reported is the CentralBusiness District. This makes 
sense because it is one of the most urban neighborhoods, so there is a high crime
rate. This could be a good option to intially rule out because in terms of 
safety, it is likely not the best. 


### Histogram of Age Groups 
```{r}
hist(policedata$AGE, xlim = c(0,90), breaks = 150, col = "slategrey", 
     xlab = "Age", main = "Histogram of Arrests")
```

### Tables of Categorical Variables
First, a relative frequency table of gender which shows that the majority of 
suspects were male.
```{r}
round(table(policedata$GENDER)/length(policedata$GENDER),3)
```
Next, a relative frequency table of race which shows that the groups with 
the largest proportion of arrests were Black (60.6%) and White (36.2). The
populations in Pittsburgh are 66.85% White, 23.21% Black/African American, 5.71%
Asian, and the rest of the population either falls into two or more race 
categories or Native American. 
```{r}
round(table(policedata$RACE)/length(policedata$GENDER),4)
```

I noticed that the dataset with traffic signs that I found also uses police 
zones and public works divisions, so this could provide an identification method 
for comparing datasets side by side. I am going to see which police zones and 
public works divisions have the highest number of traffic signs. This may be an
environmental factor that contributes to safety

## Initial Traffic Signs Exploration
```{r}
head(trafficsigns)
summary(trafficsigns)
```

Tabling police zone/incident zone and public works division in both datasets. 
```{r}

```










